

# Read clinicalt data 


```{r}
coldata_lobular <- read.csv("~/Files/clinicalLobular.tsv",sep = "\t")
```

```{r}
coldata_Duct <- read.csv("~/Files/clinicalDuct.tsv",sep = "\t")
```


## Remove duplicated Rows

```{r}
coldata_Duct <- coldata_Duct  %>% 
  distinct(case_submitter_id,.keep_all = T)
coldata_lobular <- coldata_lobular  %>% 
  distinct(case_submitter_id,.keep_all = T)
```

## Combine clinical information of both groups 

```{r}
coldata <- rbind(coldata_Duct,coldata_lobular)
```






# Make a new folder to store all the compressed files in different folder
- Use function "list.file" to find all the compressed file in each foler
- Use function "list.copy" to copy-past them into the new folder

*No need when using the data in GoogleDrive*
```{r}
setwd("/Users/margery/Desktop/data/")
dir.create("12_2_Duct")
for (dirname in dir('12_1_duct/')){  
  file <- list.files(paste0(getwd(),'/12_1_duct/',dirname),pattern = '*.counts')  
  file.copy(paste0(getwd(),'/12_1_duct/',dirname,'/',file),'12_2_Duct')  
}
```



```{r}
setwd("/Users/margery/Desktop/data/")
dir.create("12_2_Lobular")
for (dirname in dir('New_Lobular/')){  
  file <- list.files(paste0(getwd(),'/New_Lobular/',dirname),pattern = '*.counts')  
  file.copy(paste0(getwd(),'/New_Lobular/',dirname,'/',file),'12_2_Lobular')  
}
```


# To find the TCGA ID corresponding to the file name (Lobular)

```{r}
metadata <- jsonlite::fromJSON("metadata.cart.12.2Lobular.json")
naid_df <- data.frame()
for (i in 1:nrow(metadata)){
  naid_df[i,1] <- metadata$file_name[i]
  naid_df[i,2] <- metadata$associated_entities[i][[1]]$entity_submitter_id
}
colnames(naid_df) <- c('filename','TCGA_id')
```


### only chose the TCGA's first 12 characters in clinical 

```{r}
attach(naid_df)
naid_df$TCGA_id=substr(TCGA_id,regexpr("T",TCGA_id,),regexpr("T",TCGA_id)+11)  
```


```{r}
write.table(naid_df,"Duct_filename_TCGAid.txt", quote = FALSE, row.names = FALSE,col.names = F)
```






## To find the TCGA ID corresponding to the file name （Duct）
```{r}
metadata <- jsonlite::fromJSON("~/Files/metadata.cart.duct12-01.json")
naid_df <- data.frame()
for (i in 1:nrow(metadata)){
  naid_df[i,1] <- metadata$file_name[i]
  naid_df[i,2] <- metadata$associated_entities[i][[1]]$entity_submitter_id
}
colnames(naid_df) <- c('filename','TCGA_id')
```

```{r}
attach(naid_df)
naid_df$TCGA_id=substr(TCGA_id,regexpr("T",TCGA_id,),regexpr("T",TCGA_id)+11)  
```


```{r}
write.table(naid_df,"Lobular_filename_TCGAid.txt", quote = FALSE, row.names = FALSE,col.names = F)


```

# correspond the geneid and duct ?

?

```{r}
#coldata_Duct$TCGA_id <- coldata_Duct$case_submitter_id
```

```{r}
 #write.csv(coldata_Duct,"coldata_Duct.csv",row.names = F)
# write.csv(coldata_lobular,"coldata_Lobular.csv",row.names = F)
```


# After building relationship between Lobular/Duct + group + "digital serial number" by Excel

## Read this file

```{r}
library(readxl)
Lobular1<-read_excel("~/Files/Lobulargroup_id.xlsx")
Lobular1 <- as.data.frame(Lobular1)
```

## Transfer it into TXT file to do name change 

```{r}
write.table(Lobular1,"Lobulargroupchange.txt", quote = FALSE, row.names = FALSE,col.names = F)
```

```{r}

library(readxl)
Duct1<-read_excel("~/Files/Ductgroup_id.xlsx")
Duct1<- as.data.frame(Duct1)
```

```{r}
write.table(Duct1,"Ductgroupchange.txt", quote = FALSE, row.names = FALSE,col.names = F)
```

## Combind the relationship data of 2 groups and add them into clinical dataframe

```{r}
Duct_Lobular <- rbind(Duct1,Lobular1)
Col_Duct_Lobular <- merge(Duct_Lobular,coldata,by="case_submitter_id")
```

```{r}
 write.csv(Col_Duct_Lobular,"Col_Duct_Lobular.csv")
``` 
